Multicast File Transfer Protocol

### 2011-07-15 papers/paper1/paper.tex
diagram one
Finished up (for now) Implementation

\paragraph{I/O Automata}
We used the ioa framework to develop an implementation of the MFTP protocol.  I/O Automata model stateful distributed system components that can interact and be composed with each other.
They change state via transitions classified as input, output or internal actions.
Input and output actions in different automata are bound; output actions in the one serve as interrupts to trigger input actions in the other.

%%General overview of the framework and formal model.
\includegraphics[scale=0.55]{diagramOne}

%%Describe our implementation at the 50k ft view and work our way down until things are no longer interesting.
In our implementation of MFTP, we defined a basic MFTP automaton, a sender and a receiver.
The responsibilities of the MFTP automaton are to acquire[?] data and to help others acquire it.
Each MFTP automaton begins with a file, encapsulated in a File object, which is either incomplete or complete.
If the file is incomplete, the automaton generates requests for the missing fragments.
If the file is complete, the automaton may only serve the file, or it may serve the file while performing matching on it.

@@

MFTP automata receive messages via the receive input action.  If the input message is a valid fragment of its own file, it saves the fragment.
If the input message is a request for fragments of its file, it flags those fragments as having been requested.
If the input message is a match containing its file ID, it records the matching IDs for download.

The automaton holds a queue of one message to send. 
The internal actions which fill this queue are triggered periodically.
The automaton generates messages containing one requested fragment if some fragments in the file have been requested.
The fragment sent is selected at random to help avoid collision with other MFTP automata serving the same file.
The automaton generates requests if some fragments in the automaton's own file are missing.
The automaton generates match messages if it knows about any matches to its file.

The automaton may report that its file is complete using the download complete output action.

\paragraph{Matching.}
Each MFTP automaton contains one flag that determines whether it will perform matching and another that determines whether it will self-destruct when it has finished downloading its file.
If the matching flag is set, the automaton applies a function $\iota$ to the file IDs of incoming fragments to determine whether it is a fragment of a file that could be a match.
If $\iota$ is true, the automaton recursively constructs another MFTP automaton to download the potential match.
This child automaton does not perform matching.  Its self-destruct flag is set so that it will self-destruct once the potential match has been downloaded.
When the download is complete, the parent automaton applies $\mu$ to the file to determine whether it is a match.

The sending automaton uses the UDP sender built into ioa to multicast messages one at a time.
The receiving automaton uses the ioa UDP receiver.
The sender and receiver automata may be connected to more than one MFTP automaton.

\paragraph{Jam.} %%needs different header
Our implementation defines three file types, \emph{file}, \emph{meta} and \emph{query}.  A file of file type contains data from any file in the network.
A meta file contains as data the file ID of a file in the network and the name which is associated with it.
A query file contains only the name of the file which is being queried.

We wrote two programs, \emph{Share} and \emph{Get}, which use MFTP, sender and receiver automata to disseminate a file or files. %%Can one 'disseminate' a file?
Share creates two MFTP automata, \emph{file server} and \emph{meta server}.
File server is constructed with a complete file \emph{f}, and meta server is constructed with a meta file.
The meta file is generated from the fileID and name of f.
At the start, Get creates one MFTP automaton, \emph{query server}, constructed with a query file.
The query file is generated from the name of the file to download, supplied by the command line argument.

We defined a functor interface so that Share and Get could use different $\iota$ and $\mu$ functions.
In Share, meta server performs matching on the meta file and broadcasts matches to f.
Its $\iota$ returns true if the incoming file is a query file.
Its $\mu$ returns true if the contents of the downloaded query file match the name of f.
In Get, query server performs matching on the query file.
Its $\iota$ returns true if the incoming file is a meta file.
Its $\mu$ returns true if the contents of the downloaded meta file match the name of the file being queried.

Query server passes the meta files downloaded by its child automata to Get.
Using the file IDs contained in the meta files, Get constructs further MFTP automata which download the files pertaining to those file IDs.

\vspace{10 mm}

@@

\vspace{10 mm}

@@

\vspace{10 mm}
%%\begin{itemize}
%%  \item Problem
%%  \item Design forces
%%  \item Solution
%%  \item Consequences
%%\end{itemize}

>>>>

\paragraph{MFTP Automaton.}
Our implementation of MFTP uses the ioa framework.
I/O Automata model stateful distributed system components that can interact and be composed with each other.
They change state through transitions classified as input, output or internal actions.
Input and output actions in different automata are bound; output actions in the one trigger input actions in the other.

%%Describe our implementation at the 50k ft view and work our way down until things are no longer interesting.
We define a basic MFTP automaton, a sender, and a receiver.
The responsibilities of the MFTP automaton are to acquire data and to help others acquire it.
Each MFTP automaton begins with a file, encapsulated in a File object, which is either incomplete or complete.
If the file is incomplete, the automaton generates requests for the missing fragments.
If the file is complete, the automaton may serve the file, or it may serve the file while performing matching on it.

@@

MFTP automata receive messages via the receive input action.
If the input message is a valid fragment of its own file, the automaton saves the fragment.
If the input message is a request for fragments of its file, it flags those fragments as having been requested.
If the input message is a match containing its file ID, it records the matching IDs for download.

The automaton holds a queue of one message to send. 
The internal actions which fill this queue are triggered periodically.
The automaton generates messages containing one requested fragment if any fragments in the file have been requested.
The fragment sent is selected at random to help avoid collisions with other MFTP automata serving the same file.
The automaton generates requests if some fragments in the automaton's own file are missing.
The automaton generates match messages if it has recorded any matches to its file.

The automaton reports that its file is complete using the download complete output action.

\paragraph{Matching.}
Each MFTP automaton contains a flag that determines whether it will perform matching. 
It has another flag that determines whether it will self-destruct when it has finished downloading its file.
If the matching flag is set, the automaton applies the matching function $\iota$ to the file IDs of incoming fragments.
If $\iota$ is true, the automaton recursively constructs another MFTP automaton to download the potential match.
This child automaton does not perform matching.  
Its self-destruct flag is set so that it will self-destruct once the potential match has been downloaded.
When the download is complete, the parent automaton applies the matching function $\mu$ to the file to determine whether it is a match.

\paragraph{Some useful stuff.} %% We know it's rough, but what else can we do?
The sending automaton uses the UDP sender built into ioa to multicast messages one at a time.
The receiving automaton uses the ioa UDP receiver.
The sender and receiver automata may be connected to more than one MFTP automaton.

\vspace{5mm}
\includegraphics[scale=0.65]{diagramOne}

\paragraph{Jam.} %%needs different header
Our implementation defines three file types, \emph{data}, \emph{meta} and \emph{query}.  
A data file contains data from any file in the network.
A meta file contains as data the file ID of a file in the network and its name. 
A query file contains only the name of the file which is being queried.

We wrote two programs, \emph{Share} and \emph{Get}, which use MFTP, sender and receiver automata to disseminate a file or files. %%Can one 'disseminate' a file?
Share creates two MFTP automata, \emph{file server} and \emph{meta server}.
File server is constructed with a complete file \emph{f}, and meta server is constructed with a meta file.
The meta file is generated from the fileID and name of f.
At the start, Get creates one MFTP automaton, \emph{query server}, constructed with a query file.
The query file is generated from the name of the file to download, supplied by a command line argument.

We defined a functor interface so that Share and Get could use different $\iota$ and $\mu$ functions.
In Share, meta server performs matching on the meta file and broadcasts matches to f.
Its $\iota$ returns true if the incoming file is a query file.
Its $\mu$ returns true if the contents of the downloaded query file match the name of f.

\vspace{2 mm}

@@

\vspace{2 mm}

In Get, query server performs matching on the query file.
Its $\iota$ returns true if the incoming file is a meta file.
Its $\mu$ returns true if the contents of the downloaded meta file match the name of the file being queried.
Query server passes the meta files downloaded by its child automata to Get.
Using the file IDs contained in the meta files, Get constructs further MFTP automata which download the files pertaining to those file IDs.

\vspace{2.5 mm}

@@

\vspace{2 mm}

%%\begin{itemize}
%%  \item Problem
%%  \item Design forces
%%  \item Solution
%%  \item Consequences
%%\end{itemize}
